Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-02-20 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Update outline.

	%MRS3: Take a pass at reprhasing this -- important to get this right. don't start with a preposition.

	We must show that the developed molecular model is physically realistic so that we can trust conclusions drawn about structural features characteristic of the system.
	%old:To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.   
	\begin{itemize}
		\item This paper will illustrate the careful development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
		\item We are primarily interested in reproducing the conclusions about structure which can be made from SAXS experiments, predicting ionic conductivity with a reasonable comparison to experiment, and reproducing experimental density measurements.    
			\item We can simulate x ray diffraction patterns based on atomic coordinates
			\item We can predict ionic conductivity using two agreeing methods
			\item Density? - I will ask Mike to take more density measurements. It seems worthwhile     
	\end{itemize}

@@

	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
	%Twenty monomer  per pore provides a balance of structural accuracy and computational efficiency. 
	%MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item 5 layers create micellar structure
		\item Beyond 20 layers is unnecessary to get expected configuration
		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
	\end{itemize}
%MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
%BJC3: Maybe i include this in the supplemental information. I don't think a picture of the initial configuration is actually that interesting or important. I can't think of a thesis for a figure that is purely illustrative 
	FIGURE: initial configuration \\
	caption: A representative initial configuration. The pores are rotated to prevent overlaps \\
	\\
	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
	\begin{itemize}
		\item SAXS gives an idea of Pore-to-Pore distances
		\item TEM images and rejection studies give a pore size estimate
		\item To prevent unrealistic jumps during initial equilibration steps, the following equilibration scheme was adopted
			\begin{itemize}
			\item Apply position restraints to monomer head groups during energy minimization 
			\item Leave position restraints for npt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
			\item Gradually reduce force constants (by square root every 50 ps) until they are completely off
			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate
			\end{itemize}
	\end{itemize}

@@

	Proper selection of initial structural parameters results in an equilibrated model that is experimentally consistent 
	\begin{itemize}
		\item Visual perspective \\
%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
		FIGURE: shows top view and cross section (with pbcs on)\\
		%caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
		%(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
			caption: % BJC3: Attempt #2 trying to make it more thesis like. These aren't meant to do much other than show that we get, qualitatively, the same strucure described in the literature
		(a) The expected hexagonal membrane morphology is preserved upon equilibration
		(b) Straight cylindrical pore regions are present 
		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
		\item Pore to pore distance
		\begin{itemize}
			\item We know from SAXS data what the distance between pores should be
			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
			\item Simulated SAXS data
		\end{itemize}
		FIGURE - perhaps a four panel figure
		(a) Experimental Small Angle X-ray scattering data shows confirms a hexagonally packed morphology and tells us the distance between pores \\
		(b) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\  	
		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
	\end{itemize}

@@

	\begin{itemize}
		\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
		\item Stable simulations with 6 and 7 monomers have been performed which give structural characteristics consistent with experiment
		\item Stable systems have also been simulated consisting of varying numbers of monomers per layer
		\item Calculating the number density of components in the z direction has shown defined groups % will do for 7 monomers / layer and alternating monomers / layer
		\\ Figure \\
		(a) The number density of benzene ring centers in the z direction shows regions with higher concentrations of the component \\
		(b) A power spectrum of the data in (a) indicates that a new layer is defined every 4 angstroms implying that there are 5 monomers per layer.\\
		\item Even though there are defined regions of higher component density, there is still considerable variation in the position of the components (shown by the extra noise in the power spectrum)
		\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
		\item Density of components along Z axis \\
		\item There are not clear layers despite the defined layers in the starting configuration.

@@

	The arrangement of sodium counterions within the hydrophilic pore regions can be fit to a gaussian distribution. 
	\begin{itemize}
		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations under a variety of conditions suggest that ions prefer disorder within the pores. 
		\item A size exclusion mechanism has been proposed in the past, however that might no be the only force at play
		\item Ions may play a role in transport, hindering flux of solute and solvent by slowing their diffusion
		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
		\\FIGURE - plot from grant - sodium, benzene, tail densities in pores
                %MRS3: again, thesis.
		caption: The densities of sodium (blue), benzene (red), and alkyl tail carbons (cyan) surrounding the membrane pore centers indicate that each the pore region is a soup of the three components opposing the previously assumed hollow region. 
	\end{itemize}

	%BJC: New x-ray data here. Need higher resolution simulated data (working on it) and supporting experimental results first.

	The model gives reasonable estimates of ionic conductivity.
	\begin{itemize}
		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory
		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system
		\item Two methods used to for prediction
		\item Nernst Einstein Relation:
		\begin{itemize}
			\item Widely used equation for estimating ionic conductivity
			\item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
			\item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
			\item Concentration is concentration of ions in the whole membrane, not just channels
		\end{itemize}
		\item Collective Diffusion:
		\begin{itemize}
			\item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
			\item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
			\item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
			\item A similar model has been derived and validate to predict water permeability using equilibrium simulations
			\item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores. One would expect single channel IC to be much larger than the bulk membrane
		\end{itemize}                    
	\end{itemize}
	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error
	\\

>>>>

	%MRS3: Take a pass at reprhasing this -- important to get this right. don't start with a preposition.
        %MRS4: maybe ``consistent with physical observations?''
	We must show that the developed molecular model is physically realistic so that we can trust conclusions drawn about structural features characteristic of the system.
	%old:To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.   
	\begin{itemize}
		\item This paper will illustrate the careful development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
		\item We are primarily interested in reproducing the conclusions about structure which can be made from SAXS experiments, predicting ionic conductivity with a reasonable comparison to experiment, and reproducing experimental density measurements.    
			\item We can simulate x ray diffraction patterns based on atomic coordinates
			\item We can predict ionic conductivity using two agreeing methods
			\item Density? - I will ask Mike to take more density measurements. It seems worthwhile     
	\end{itemize}

@@

	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
	%Twenty monomer  per pore provides a balance of structural accuracy and computational efficiency. 
	%MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
        %MRS4: OK, but note that we will need to expand this to be enough convincing qualitative information.  Could also use quantitaitve information about how far from the surface you see the effects of the surface.
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item 5 layers create micellar structure
		\item Beyond 20 layers is unnecessary to get expected configuration
		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
	\end{itemize}
%MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
%BJC3: Maybe i include this in the supplemental information. I don't think a picture of the initial configuration is actually that interesting or important. I can't think of a thesis for a figure that is purely illustrative 
	FIGURE: initial configuration \\
%MRS4: I'm not quite sure what ``pores are rotated'' means.
	caption: A representative initial configuration. The pores are rotated to prevent overlaps \\
	\\
	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
	\begin{itemize}
		\item SAXS gives an idea of Pore-to-Pore distances
		\item TEM images and rejection studies give a pore size estimate
		\item To prevent unrealistic jumps during initial equilibration steps, the following equilibration scheme was adopted
			\begin{itemize}
			\item Apply position restraints to monomer head groups during energy minimization 
			\item Leave position restraints for npt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
			\item Gradually reduce force constants (by square root every 50 ps) until they are completely off
			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate
			\end{itemize}
	\end{itemize}

@@

	Proper selection of initial structural parameters results in an equilibrated model that is 
%MRS4: change to be more specific.
consistent with several key experimental measurements.
%experimentally consistent 
	\begin{itemize}
		\item Visual perspective \\
%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
		FIGURE: shows top view and cross section (with pbcs on)\\
		%caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
		%(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
			caption: % BJC3: Attempt #2 trying to make it more thesis like. These aren't meant to do much other than show that we get, qualitatively, the same strucure described in the literature
		(a) The expected hexagonal membrane morphology is preserved upon equilibration
		(b) Straight cylindrical pore regions are present 
		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
		\item Pore to pore distance
		\begin{itemize}
			\item We know from SAXS data what the distance between pores should be
			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
			\item Simulated SAXS data
		\end{itemize}
%MRS4: seems like an awful lot to put into one figure, even with multiple panels.
		FIGURE - perhaps a four panel figure
		(a) Experimental Small Angle X-ray scattering data shows confirms a hexagonally packed morphology and tells us the distance between pores \\
		(b) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\
%MRS4: I think we will need to be much more specific about how the simulated x-ray diffraction pattern matches experimental masurement, and the different features that do match.  	
		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
	\end{itemize}

@@

	\begin{itemize}
		\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
		\item Stable simulations with 6 and 7 monomers have been performed which give structural characteristics consistent with experiment
		\item Stable systems have also been simulated consisting of varying numbers of monomers per layer
		\item Calculating the number density of components in the z direction has shown defined groups % will do for 7 monomers / layer and alternating monomers / layer
		\\ Figure \\
		(a) The number density of benzene ring centers in the z direction shows regions with higher concentrations of the component \\
		(b) A power spectrum of the data in (a) indicates that a new layer is defined every 4 angstroms implying that there are 5 monomers per layer.\\
%MRS4: make it clear that this is calculated from the equilbrium distance. 
%MRS5: in general, there should be some information we can see looking directly at the density, not just the power spectrum.  We will need to convince people there is something there.
		\item Even though there are defined regions of higher component density, there is still considerable variation in the position of the components (shown by the extra noise in the power spectrum)
		\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
		\item Density of components along Z axis \\
%MRS4: we need to reconcile the idea ``there are 5 monomers per layer'' and ``there are not clear layers''.  It will be hard for me to reconcile them without knowing a bit more information.
%MRS4: question: are the monomers themselves in a helical shape (not just the head groups?)
		\item There are not clear layers despite the defined layers in the starting configuration.

@@

	The arrangement of sodium counterions within the hydrophilic pore regions can be fit to a gaussian distribution. 
	\begin{itemize}
		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations under a variety of conditions suggest that ions prefer disorder within the pores. 
		\item A size exclusion mechanism has been proposed in the past, however that might no be the only force at play
		\item Ions may play a role in transport, hindering flux of solute and solvent by slowing their diffusion
		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
		\\FIGURE - plot from grant - sodium, benzene, tail densities in pores
                %MRS3: again, thesis.
%MRS4: we should think a little bit about whether which parts of the alkyl tail we plot, and whether to just focus on the core (ignoring the first 5 A or so from each end).  Depends on what we are trying to show.
		caption: The densities of sodium (blue), benzene (red), and alkyl tail carbons (cyan) surrounding the membrane pore centers indicate that each the pore region is a soup of the three components opposing the previously assumed hollow region. 
	\end{itemize}

	%BJC: New x-ray data here. Need higher resolution simulated data (working on it) and supporting experimental results first.
        %MRS4 got it.  Will need to do some work on making this clear.

	The model gives reasonable estimates of ionic conductivity.
	\begin{itemize}
		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory
		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system
                %MRS4: not sure you describe how to do that here.
		\item Two methods used to for prediction
		\item Nernst Einstein Relation:
		\begin{itemize}
			\item Widely used equation for estimating ionic conductivity
			\item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
			\item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
			\item Concentration is concentration of ions in the whole membrane, not just channels
		\end{itemize}
		\item Collective Diffusion:
		\begin{itemize}
			\item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
			\item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
			\item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
			\item A similar model has been derived and validate to predict water permeability using equilibrium simulations
			\item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores. One would expect single channel IC to be much larger than the bulk membrane
		\end{itemize}                    
	\end{itemize}
	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error
	\\
